***De novo* clustering methods out-perform reference-based methods for assigning 16S rRNA gene sequences to operational taxonomic units**

### 2015-10-12 Schloss_Cluster_PeerJ_2015.Rmd
Remove slow to calculate values from Rmd file

n_miseq_seqs <- nrow(read.table(file="data/miseq/miseq.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.redundant.summary"))

n_unique_miseq_seqs <- nrow(read.table(file="data/miseq/miseq.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.summary"))

n_groups <- ncol(read.table(file="data/miseq/miseq.trim.contigs.good.unique.good.filter.unique.precluster.denovo.uchime.pick.pick.count_table")) - 2 #subtract 2 to remove the sequence name and total number of sequences

>>>>

miseq_info <- read.table(file="data/miseq/miseq.seq.info", row.names=1, quote=F)
n_groups <- miseq_info["n_groups",1]
n_miseq_seqs <- miseq_info["n_miseq_seqs",1]
n_unique_miseq_seqs <- miseq_info["n_unique_miseq_seqs",1]
